Bayesian Networks for Assessing Environmental Sustainability in Australian Vineyards

### 2024-06-24 article.tex
discussion progress

This investigation highlighted the key factors of Australian winegrowing that contribute to  environmental sustainability through the lens of graphical models. These models have established the intricate, and interconnected nature of various influences on environmental sustainability in Australian winegrowing; where a keener understanding of how these factors both interact and effect one another from the perspective of research and industry is illustrated.

Of these factors, the BN was able to show the critical nature that water played as one of the most interconnected variables. Furthermore, how the influence of water use reached multiple variables that reflected different operational decisions within a vineyard such as tractor use, disease and pest prevention, as well as management strategies for soil. This finding aligns with water being the lifeblood of agriculture, essential for both the health of the vines and the broader ecosystem, especially within Australia's dry climate.

Of further significance was the management of pests and diseases, market pressures and climate. With these external influencing being prominently connected to vineyard operations through their connection to factors such as fuel, tractor, water and electricity use. Particularly, climate was an interface between water and pest/disease, due to it being a determining factor in temperature and water availability.

Climate and weather conditions are shown to be significant determinants of environmental sustainability in viticulture. The BN models capture the complexity of these factors, demonstrating how they influence water availability, pest and disease pressures, and overall vineyard health. Understanding these interactions is vital for developing adaptive management strategies that can cope with climate variability and change.
Comparative Analysis with Existing Literature

Such elements being used in some operational responses to things such as disease through the use of agrochemicals. Where, environmental sustainability was highly sensitive to as a factor; the case study highlighting its direct influnce on environmental sustainability. A major concern from the industry panel was that, while necessary for maintaining vine health and productivity, excessive or inappropriate agrochemical use can lead to major negative environmental impacts. The model emphasised the need for balanced and regulated agrochemical practices; and especially for those to be followed appropriately.

The findings from this study are consistent with the existing literature on sustainability in viticulture, which also identifies water management, pest and disease control, economic pressures, and climate conditions as key factors. However, the BN models provide a more structured and detailed map of how these factors interact, offering a clearer understanding of their interdependencies and relative importance.

The study's results align well with previous research, reinforcing the significance of the identified factors. For instance, the critical role of water management is well-documented in the literature, and this study further elucidates its central position within the network of sustainability factors.

While the existing literature provides a broad understanding of sustainability in viticulture, this study offers novel insights through the use of BN models. These models reveal specific pathways and interactions that are less apparent in traditional analyses, highlighting areas where targeted interventions could have the most significant impact.

The comparison with previous research highlights how the BN approach can expand our understanding of sustainability by integrating expert knowledge and empirical data into a coherent framework. This method not only confirms known relationships but also uncovers new connections and sensitivities that are critical for informed decision-making.

@@

>>>>

% Needed references are currently highlighted as TODO:

This investigation highlighted the key factors of Australian winegrowing that contribute to  environmental sustainability through the lens of graphical models. These models have established the intricate, and interconnected nature of various influences on environmental sustainability in Australian winegrowing. A keener understanding of how these factors both interact and effect one another from the perspective of research and industry is illustrated within these models, with a major outcome being the highlighting the critical nature that water use plays. As one of the most interconnected variables, the influence of water use reaches almost every variable, with its connection to operational decisions being reflected within its connection to other factors such as tractor use, disease and pest prevention, as well as management strategies for soil. This finding aligns with water being the lifeblood of agriculture, essential for both the health of the vines and the broader ecosystem, especially within Australia's dry climate.

Of further significance was the management of pests and diseases, market pressures and climate. With these external influences being prominently connected to vineyard operations through their connection to factors such as fuel, tractor, water and electricity use. Particularly, climate acted as an interface between water and pest/disease, due to it being a determining factor in temperature and water availability which are highly influential to pests and disease TODO:. Of the greatest concern to climate is how it influences water availability, pest and disease pressures, and overall vineyard health. Understanding these interactions is vital for developing adaptive management strategies that can cope with climate variability and change TODO:. In a more general sense climate and weather conditions are shown within the literature to be significant determinants of a variety of factors within vineyards such as yield, erosion, and are further determinants of chosen grape varieties TODO:. The BN models capture the complexity of how climate can propagate to these considerations through other factors; as well as how these other factors are connected.

the case study highlighted the direct influence on environmental sustainability, where it was found to be the most sensitive to elements used in operational responses to factors such as disease through the use of agrochemicals. A major concern from the industry panel was, that while necessary for maintaining vine health and productivity, excessive or inappropriate agrochemical use can lead to major negative environmental impacts. The model emphasised the need for balanced and regulated agrochemical practices; and especially for those to be followed appropriately. TODO: A literature review regarding this does here TODO:

@@

The findings from this study are consistent with the existing literature on sustainability in viticulture, which also identifies water management, pest and disease control, economic pressures, and climate conditions as key factors. However, the BN models provides structure to the broader way of how these factors interact, offering a clearer understanding of their interdependencies and relative importance. Many of these singular relationships are well defined within literature studies such as TODO:.

While the existing literature provides exceptional detailed understanding of many mechanisms behind the relationships explored within this study. The BN allows the further exploration of the peripheral connections beyond these relationships to be further considered. A strength behind the use of Bayesian Network is the ability to replace edges between nodes with any analysis that allows for the derivation of a posterior from some input prior; allowing for the Bn to be used as a framework that can further integrate other studies results into these relationships.
